Document Embedding for Scientific Articles:\newline A validation of word embeddings

### 2018-07-24 Paper/Parts/Discussion/Discussion.tex
new paper start

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Results analysis}

\subsubheader{Best performers}
The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles. For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which is 1 median rank higher on the abstracts, and equal on the titles.

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles. The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, containing more tokens than the tile, thus improving the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance on our data. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, but we did not investigate this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
\clearpage
\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. This result indicates that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase of performance compared to the TF-IDF embedding, or none at all. However, the rank increases, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results: higher vocabulary sizes give better performance. 
\begin{jumpin}
\subsubsubheader{Rank distribution}
However, Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. The rank distribution of the limited TF-IDF embeddings show the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performers, indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
\end{jumpin}
The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. The removal of titles and abstracts results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles). This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles. The abstracts, on the other hand, contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. 
If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one. We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, its memory usage is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration (based on memory usage) we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory. This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the word occurrence information.

\subsubheader{Journal plots}
Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the journals in the so-called "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this Figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four Figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. The interactive version furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data. They can therefore show human defined/understandable groups in their plot, while we use the k-means algorithm to create the groupings based on the embeddings.

\subheader{Improvements}
This research shows that even though the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts. Earlier research already proposed improvements to the word embeddings. \citet{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While the improvement looks promising, we have to keep in mind that our task differs from earlier tasks. We do not categorize on two categories but more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories. These are the area's in which the classification algorithm is "in doubt" and could reasonably assign the article to both journals. The number of these grey areas increase given more categories. \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task. \citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations. Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score. We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
Even though much research has been done, we have not been able to find published results which are directly comparable to our results. This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier work\cite{wang2016linked}. Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\section{Discussion}
\subsection{Results analysis}
\subsubsection{Best performers}
The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low (1 median rank on abstract and 3 median ranks on the titles). For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings.
\subsubsection{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles. The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, containing more tokens than the tile, thus improving the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise.
\subsubsection{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding on median and average ranking. This result indicates that the noise reduction is too much, it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase of performance compared to the TF-IDF embedding, or none at all. However, the rank increases, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results: higher vocabulary sizes give better performance. 
\begin{jumpin}
\textit{Rank distribution}.
However, Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. The rank distribution of the limited TF-IDF embeddings show the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performers, indicating a better performance on the top-1 articles compared to the other sets.
\end{jumpin}
The rank distribution seems to indicate that the cut-off was effective, but not for our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding\footnote{This indicates that he 1K-6K embedding removed some articles entirely from the dataset.}.
\subsubsection{TF-IDF \& embeddings}
Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows: The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles). This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles. The abstracts, on the other hand, contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. \\
If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well, this can be seen in our data. We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.
\subsubsection{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, its memory usage is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
\end{document}

### 2018-07-24 Paper/Parts/Future_work/Future_work.tex
new paper start

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focused on the quality of word embeddings on academic texts. To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings. Future work may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.

\subheader{Method differences}
\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods. They state that the global/hyperparameters of the various methods mainly cause the difference in performance. In this research, we did not look at the comparison between various models and (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance. Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics. It should be noted however that Levy et al. base their conclusions on word similarity and word analogy tasks, and not on categorization. This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.

\subheader{Intelligent cutting}
A better way of cutting could improve the quality of the embeddings. This improvement might be achieved by cutting the center of the vector space out before normalization. This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum before normalization. Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

\subheader{Text combination}
To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text. This should be possible since the title and the abstract per article share a common topic. We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best used for the embeddings and TF-IDF.

\subheader{TF-IDFs performance point}
In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts. This leads to the question, how do token count and unique token count relate for TF-IDF? Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform? If this relation is found,  we could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, saving time and costs.

\subheader{Reversed word pairs}
At this point, there are no domain-specific word pair sets available. However, as we demonstrated, we can still test the quality of word embeddings. Once we established that we have word vectors of high quality, could we create word pairs from the embeddings? If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use. These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.

\subheader{Historical overview}
We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles for one year. This gives insight into the currently popular research field, indicated by dense areas on the plot. If we would create this plot over multiple years, and then show these years in chronological order, we should be able to see the evaluation of research fields in time, giving more insight in shifting interests and the development of new research areas.

\subheader{TF-IDF top cut-off}
In our research, we used a dataset from which we removed the top 1k words, together with everything beyond 6k. This dataset did not perform well in our research; future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance. Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance since a set with the top 5k words performed better than the 1k till 6k words set.

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search queries consist of a small number of tokens (the average google query size was 4 in 2008\footnote{According to Brian Ussery (01/02/2008): \url{https://www.beussery.com/blog/index.php/2008/02/google-average-number-of-words-per-query-have-increased/}.}). Our research showed that embeddings perform better in a situation with a low amount of tokens. Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from the word-embedding space into the TF-IDF space. Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
\clearpage
\subheader{Pre-categorization}
Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figures~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}). This knowledge could be used to pre-process given texts, creating a two-step search. This method would first categorize the given article into a field and then search in the limited set of journals for the best fit. This has two advantages: (a) we predict the field of the article, giving additional information to a user and (b) once an article is inside a certain domain, ambiguous words between domains (i.e. cloud for computer science and meteorology) are eliminated. The domain specific embeddings have not been trained with the other embeddings, thus they do not contain (cross-domain) ambiguity. A possible downside of this approach is the need for data within each domain, because the embeddings are created on two levels: cross-domain for domain categorization and in-domain for journal categorization. The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions. In a situation where there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization. The goal is to have multiple separate vector spaces, for this, it does not matter if the "domains" are well-interpretable or make sense to humans.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Future work}
\subsection{Intelligent cutting}
A better way of cutting could improve the quality of the embeddings. This improvement might be achieved by cutting the center of the vector space out before normalization. All words which are generic are in the center of the spectrum, removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other texts. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
\subsection{TF-IDFs performance point}
In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts. This leads to the question, how do token count and unique token count relate for TF-IDF? Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform? If this relation is found, one could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, reducing costs.
\subsection{Reversed word pairs}
At this point, there are no domain-specific word pair sets available. However, as we demonstrated, we can still test the quality of word embeddings. Once one has established that the word vectors are of high quality, could one create word pairs from the embeddings? If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use.
\end{document}

### 2018-07-24 Paper/Parts/Research_results/Research_results.tex
new paper start

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
In this chapter the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in Chapter 6: Discussion.
\subheader{Ranking}
The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
\clearpage
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\end{figure}
\clearpage
\subheader{Rank distribution}
Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The Figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}. The Y-axis of the two Figures shows the fraction of the total number of articles. Due to this, all sets will have a maximum of 1. When 1 is hit, the graph stagnates since the dataset has reached the maximum fraction. The X-axis plots the ranks of the articles. These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} which show average and median ranks.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set}\label{figure:titleDistribution}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
\end{figure}

\clearpage
\subheader{F1-Score}
Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1. We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e. Figure~\ref{figure:f1Title}, tfidf\_5k\_5k and tfidf\_embedding
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_avg_f1}

@@

\begin{figure}[htb]
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}

@@

\clearpage
\subheader{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}. It furthermore shows the absolute hit percentage of the title and the abstracts, i.e. the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking. The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}. Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
\begin{table}[hbt]

@@

\subheader{Journal relatedness plot}
We created four seperate journal plots, Figures~\ref{figure:titlePlotNormal} and~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} and~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings. The journals are color-marked by publisher. Red is Wiley, lime is Elsevier and blue is Springer Nature. The grey points are other or not-specified publishers.
Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups. The bottom right of the plot shows the names of the journals closest to the center of the group. While most names state the topic of the research field, two do not. These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies. The k-means algorithm ran on the 300-dimensional vectors, while the plot shows the 2-dimensional vectors. In the title-based Figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph. In the abstract-based Figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k} (abstract-based). The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures. Although the presented figures give sufficient insight for the purpose of this thesis.
\begin{landscape}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_normal}
\caption{Journal plot of title embeddings, grouped by publisher}\label{figure:titlePlotNormal}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_normal}
\end{center}
\caption{Journal plot of abstract embeddings, grouped by publisher}\label{figure:abstractPlotNormal}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_grouped}
\end{center}
\caption{Journal plot of title embeddings, k-means grouped}\label{figure:titlePlotGrouped}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_grouped}
\end{center}
\caption{Journal plot of abstract embeddings, k-means grouped}\label{figure:abstractPlotGrouped}
\end{figure}
\end{landscape}
\end{document}

>>>>

\documentclass[../../paper.tex]{subfiles}
\begin{document}
\section{Research results}
In this section the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in section 4: Discussion.
\subsubsection{Ranking}
The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
\subsubsection{Rank distribution}
Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The Figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective figures (Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}).
\subsubsection{F1-Score}
Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1.
\subsubsection{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}. It furthermore shows the absolute hit percentage of the title and the abstracts, i.e. the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking. The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}. Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.
\FloatBarrier
\includegraphics[width=4.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\includegraphics[width=4.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\includegraphics[width=4.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set, Y-axis shows the fraction of articles.}\label{figure:titleDistribution}
\includegraphics[width=4.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set, Y-axis shows the fraction of acticles.}\label{figure:abstractDistribution}
\includegraphics[width=4.5in]{Plots/Title_avg_f1}

@@

\includegraphics[width=4.5in]{Plots/Abstract_avg_f1}

@@

\FloatBarrier
\begin{table}

@@

\FloatBarrier
\end{document}
